---
title: "Brazil surf spot carbon valuation"
author: "Kort Alexander"
date: "2022-11-08"
output: html_document
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(janitor)
library(broom)
```

# Data input

```{r}
all_spots <- read_csv(here("data", "all_spots.csv")) %>% 
  clean_names()
ws_plus_sl <- read_csv(here("data", "ws_plus_sl.csv")) %>% 
  clean_names()
```

# Initial stock valuations

SCC values for 2023 from https://19january2017snapshot.epa.gov/climatechange/social-cost-carbon-technical-documentation_.html 

```{r}
SCC_2.5_2023 <- 65
SCC_3_2023 <- 44
SCC_5_2023 <- 13
all_spots <- all_spots %>% 
  mutate(stock_value_10km_2.5 = sum_10km * SCC_2.5_2023) %>% 
  mutate(stock_value_10km_3 = sum_10km * SCC_3_2023) %>% 
  mutate(stock_value_10km_5 = sum_10km * SCC_5_2023) %>% 
  mutate(stock_value_1km_2.5 = sum_1km * SCC_2.5_2023) %>% 
  mutate(stock_value_1km_3 = sum_1km * SCC_3_2023) %>% 
  mutate(stock_value_1km_5 = sum_1km * SCC_5_2023)
ws_plus_sl <- ws_plus_sl %>% 
  mutate(stock_value_10km_2.5 = sum_10km * SCC_2.5_2023) %>% 
  mutate(stock_value_10km_3 = sum_10km * SCC_3_2023) %>% 
  mutate(stock_value_10km_5 = sum_10km * SCC_5_2023) %>% 
  mutate(stock_value_1km_2.5 = sum_1km * SCC_2.5_2023) %>% 
  mutate(stock_value_1km_3 = sum_1km * SCC_3_2023) %>% 
  mutate(stock_value_1km_5 = sum_1km * SCC_5_2023)
```

# Amount of carbon sequestered out to 2050

Annual sequestration will be equal to total sequestered carbon by 2050 divided by 27 years because sequestration is linear

```{r}
all_spots <- all_spots %>% 
  mutate(annual_seq_10km = sqtd_10km / 27) %>% 
  mutate(annual_seq_1km = sqtd_1km / 27)
ws_plus_sl <- ws_plus_sl %>% 
  mutate(annual_seq_10km = sqtd_10km / 27) %>% 
  mutate(annual_seq_1km = sqtd_1km / 27)
```

# Creating SCC table

Values from https://19january2017snapshot.epa.gov/climatechange/social-cost-carbon-technical-documentation_.html

```{r}
SCC_table <- data.frame(SCC_2.5 = c(65, 66, 68, 69, 70, 71, 72, 73, 74, 75, 76, 77, 78, 79, 81, 82, 83, 84, 85, 86, 87, 88, 89, 90, 92, 93, 94, 95),
                        SCC_3 = c(44, 45, 46, 47, 48, 49, 49, 50, 51, 52, 53, 54, 55, 56, 57, 58, 59, 60, 61, 61, 62, 63, 64, 65, 66, 67, 68, 69),
                        SCC_5 = c(13, 13, 14, 14, 15, 15, 15, 16, 16, 17, 17, 18, 18, 19, 19, 20, 20, 21, 21, 22, 22, 23, 23, 24, 24, 25, 25, 26))
```

# Sequestration value function

```{r}
seq_value <- function(annual_seq, r, num_years){
  SCC_values <- case_when(r == 0.025 ~ SCC_table$SCC_2.5,
                          r == 0.03 ~ SCC_table$SCC_3,
                          r == 0.05 ~ SCC_table$SCC_5)
  sum_values <- 0
  for(i in 1:num_years)
  {
    value = (SCC_values[i] * annual_seq) / (1 + r)^i
    sum_values <- sum_values + value
  }
  return(sum_values)
}
```

# Calculating sequestration value for each surf spot

```{r}
all_spots <- all_spots %>% 
  mutate(seq_value_2050_2.5_10km = seq_value(annual_seq_10km, 0.025, 27)) %>% 
  mutate(seq_value_2050_3_10km = seq_value(annual_seq_10km, 0.03, 27)) %>% 
  mutate(seq_value_2050_5_10km = seq_value(annual_seq_10km, 0.05, 27)) %>% 
  mutate(seq_value_2050_2.5_1km = seq_value(annual_seq_1km, 0.025, 27)) %>% 
  mutate(seq_value_2050_3_1km = seq_value(annual_seq_1km, 0.03, 27)) %>% 
  mutate(seq_value_2050_5_1km = seq_value(annual_seq_1km, 0.05, 27))
ws_plus_sl <- ws_plus_sl %>% 
  mutate(seq_value_2050_2.5_10km = seq_value(annual_seq_10km, 0.025, 27)) %>% 
  mutate(seq_value_2050_3_10km = seq_value(annual_seq_10km, 0.03, 27)) %>% 
  mutate(seq_value_2050_5_10km = seq_value(annual_seq_10km, 0.05, 27)) %>% 
  mutate(seq_value_2050_2.5_1km = seq_value(annual_seq_1km, 0.025, 27)) %>% 
  mutate(seq_value_2050_3_1km = seq_value(annual_seq_1km, 0.03, 27)) %>% 
  mutate(seq_value_2050_5_1km = seq_value(annual_seq_1km, 0.05, 27))
```

# Combining lat and long into two columns

```{r}
all_spots <- all_spots %>% 
  mutate(new_lat = case_when(!is.null(lat) & lat != 0 ~ lat,
                             wannasurf != 0 ~ wannasurf,
                             manually_a != 0 ~ manually_a)) %>% 
  mutate(new_long = case_when(!is.null(lon) & lon != 0 ~ lon,
                              wannasurf1 != 0 ~ wannasurf1,
                              manually_1 != 0 ~ manually_1))
ws_plus_sl <- ws_plus_sl %>% 
  mutate(new_lat = case_when(!is.null(lat) & lat != 0 ~ lat,
                             wannasurf != 0 ~ wannasurf)) %>% 
  mutate(new_long = case_when(!is.null(lon) & lon != 0 ~ lon,
                              wannasurf1 != 0 ~ wannasurf1))
```

# Plots

```{r}
ggplot(all_spots, aes(x = new_lat, y = sum_10km)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Latitude (degrees)", y = "Carbon stored in mangrove (tonnes)", caption = "") +
  theme_minimal()
ggplot(all_spots, aes(x = sum_10km)) +
  geom_histogram() +
  theme_minimal() +
  labs(x = "Carbon stored in mangrove (tonnes)", y = "Count")
```

